\newpage
\addcontentsline{toc}{section}{参考文献}
\begin{thebibliography}{99}

  \bibitem{meti_robot} 経済産業省，自動配送ロボットの将来像を取りまとめました
  \url{https://www.meti.go.jp/press/2024/02/20250226002/20250226002.html}
  %
  \bibitem{idou}青柳 誠司, 佐藤 伸仁, 山本 恭輝, 高橋 智一, 鈴木 昌人, "移動ロボットの移動
  障害物回避に関するファジィルールの学習 ポテンシャル法, 強化学習法との比較,"
  システム制御情報学会論文誌, vol. 34, no. 8, pp. 209–218, 2021.
  
  \bibitem{hriaoka} 平岡 翔，”ポテンシャル法における停留問題の回避，および効率的な経路生成手法”，東京都市大学2022年度卒業論文(2022)
  %
  \bibitem{koike} 小池 基也，”A*探索法を組み込んだ静止障害物に対するポテンシャル法の回避方法”，東京都市大学2023年度卒業論文(2023)
  %------%
  %
  \bibitem{enokida} 榎田 日和，”速度推定機能を組み込んだポテンシャル法による動的障害物の回避”，東京都市大学2024年度卒業論文(2024)

\bibitem{toyota} 
トヨタの安全技術, https://toyota.jp/safety/ (2023)

\bibitem{RRT1}
Z. Feng, S. Chen, Y. Chen and N. Zheng; Model-Based Decision Making With Imagination for Autonomous Parking; 2018 IEEE Intelligent Vehicles Symposium (IV), pp. 2216-2223, Changshu, China (2018)

\bibitem{RRT2}
M. Kim, J. Ahn and J. Park; TargetTree-RRT*: Continuous-Curvature Path Planning Algorithm for Autonomous Parking in Complex Environments; IEEE Transactions on Automation Science and Engineering, Vol.21, no.1, pp. 606-617 (2024) 

\bibitem{clothoid}
Dae Jung Kim, Chung Choo Chung; Automated Perpendicular Parking System With Approximated Clothoid-Based Local Path Planning; IEEE Control Systems Letters ,Vol.5,pp.1940-1945(2021)

\bibitem{clothoid2}
Juncheng Wang,Shengqin Li; Parallel Parking Path Planning in Narrow Space Based on a Three-Stage Curve Interpolation Method; IEEE Access, Vol.11, pp.93841-93851 (2023)

\bibitem{minR}
Hongbo Gao, Juping Zhu, Xinde Li, Yu Kang, Jiehao Li, Hang Su; Automatic Parking Control of Unmanned Vehicle Based on Switching Control Algorithm and Backstepping；
IEEE/ASME TRANSACTIONS ON MECHATRONICS，
Vol.27, No.3, pp.1233–1243 (2022)

\bibitem{minR2}
Jian-Min Wang, Sen-Tung Wu, Chao-Wei Ke, BoKai Tzeng; Parking Path Programming Strategy for Automatic Parking System; Vehicle Engineering(VE), Vol.1, No.3, pp.57–63 (2013)

\bibitem{ogata}
緒方涼,大屋英稔,星義克; 円弧と直線を用いた駐車経路生成手法; 第66回自動制御連合講演会講演論文集,66巻,pp. 1122-1125 (2023)

\bibitem{Ackerman}
Takahiko TSUJISAWA; A Proposal of Path Planning Method for a Four-Wheeled Vehicle in Automatic Parking System; 日本機械学会論文集(C 編), 73 巻729 号, pp. 1273–1278 (2007)

 \bibitem{model_car}
トヨタ自動車, “ヤリス”. https://toyota.jp/yaris/(2023/5/9) 

\end{thebibliography}
